COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-10-09 main.tex
Add discussion of figure 6

>>>>

As is seen in figure \ref{fig:long_ph}, the relatively fast precession rates induced by the mean motion resonances overpower the secular forcing by Jupiter and randomize the orientation of orbits near the nominal resonance locations. Of course, this difference in longitude of perihelion of bodies inside and outside of resonance is only present in the EJ simulation because the Jupiter imposes zero forced eccentricity on the disk when it has a circular orbit. Figure \ref{fig:m_hist} provides another view of the difference in collision statistics inside and outside and of resonance. The top row shows the mean anomaly of bodies at the moment that they undergo a collision. The left side corresponds to collisions that occur inside of the 2:1 MMR and the right side corresponds to collisions that occur with a semimajor axis between 2.7 and 2.8 AU, which is meant to well away from the influence of any resonances. The semimajor axis window size in the right hand panel is chosen so that both histograms contain the same total number of collisions. The bottom row shows the difference in the mean anomaly between pairs of bodies at the moment that they collide.

In this figure, the most notable difference between the collision statistics inside and outside of resonance is that collisions inside of resonance preferentially happen at perhielion. In addition, the two bodies that collide tend to be at a similar orbital phase. Outside of resonance, however, there are no significant trends in the mean anomaly at collision or in the mean anomaly difference. The difference in collision statistics between these two regions of the disk can be explained in the following way: for $\approx$ 100 km bodies, gravitational focusing plays a significant role in controlling the collision rate. In this regime, the collision rate is given by equation \ref{eq:safronov}, is larger for small relative velocities $v_{p}$ between planetesimals. At perihelion, relative velocities between planetesimals are largest (wait, this is backwards, why do collisions tend to happen at perihelion?). When the longitude of perhelia for adjacent orbits are aligned, which is true away from the resonances, bodies will always tend to have similar relative velocities, regardless of orbital phase. Therefore, the collision rate should no longer vary with mean anomaly, which is exactly what is shown in the top right panel of figure \ref{fig:m_hist}. (But shouldnt you see points clustered around deltaM = 0 in the bottom right panel then?)

\subsection{Comparison With Analytic Safronov Collision Rate}\label{sec:saf}
